---
title: "Electricity Consumption Prediction"
---

This project applied descriptive and statistic analysis in R to determine key variables to analyze Singapore household energy usage among different housing types, areas and periods.

```{r,warning=FALSE,message=FALSE,include=FALSE}
library(readxl)
library(tidyverse)
library(ggplot2)
library(shiny)
library(rsconnect)
```

## Electricity Consumption by Room Type (2005-2022)

```{r,warning=FALSE,message=FALSE}
mydata <- read_excel("damand data/DemandSideData.xlsx",sheet='Housetype_consumption')
my_colors <- c("1-room / 2-room" = "tan", "3-room" = "green", "4-room" = "lightblue", "5-room and Executive" = "blue","Private Apartments and Condominiums" = "coral","Landed Properties" = "pink")
ggplot(mydata, aes(x = Year , y = AverageAnnualHouseholdElectricityConsumption,color=Roomtype)) +
  geom_point()+
  labs( 
    y='Annual Average Consumption(kWh)',x='Year')+
  geom_smooth(method=lm, se=F)+ scale_color_manual(values = my_colors)
```

## Household Size by Room Type (2005-2022)

```{r,warning=FALSE,message=FALSE}
library(readxl)
DemandSideData <- read_excel("damand data/DemandSideData.xlsx", 
                             sheet = "Householdsize")
data_long <- tidyr::gather(DemandSideData, key = "Room_type", value = 'Household_size', -Year)
ggplot(data_long, aes(x = Year, y = Household_size, color = Room_type)) +
  labs(
    x='Year')+
  geom_line()
```

## Number of Household by Room Type

```{r,warning=FALSE,message=FALSE}
Household_number <- read_excel("damand data/DemandSideData.xlsx", 
                               sheet = "Household_number")
data <- tidyr::gather(Household_number, key = "Room_type", value = 'Household_number', -Year)
ggplot(data, aes(x = Year, y = Household_number/1000, color = Room_type)) +
  geom_line()+
  labs(y='Number of household(1/1000)',
       x='Year')+
  scale_y_continuous(labels = scales::comma)
```

## Household Electricity Consumption by Region (2005-2022)

```{r,warning=FALSE,message=FALSE}

library(tmap)
library(sf)
library(readxl)
library(leaflet)



region <- read_excel("damand data/Consumption_region.xlsx", 
                     sheet = "Consumption_region")

shapefile <- st_read("damand data/shapefile/MP14_SUBZONE_NO_SEA_PL.shp") 

region_summary <- region %>%
  group_by(Region) %>%
  summarize(avg_annual_consumption = mean(Monthly_Consumption) * 12)

data_map_area <- inner_join(shapefile,region_summary, by= c("PLN_AREA_N" = "Region"))

tmap_options(check.and.fix = TRUE)
tmap_mode("view")
qtm(data_map_area, fill="avg_annual_consumption", fill.id = "PLN_AREA_N")
```

## Annual Household Electricity Consumption (2005-2021)

```{r,warning=FALSE,message=FALSE}
library(readxl)
Demand_Data <- read_excel("damand data/DemandSideData.xlsx", 
                          sheet = "Consumption")
ggplot(Demand_Data, aes(x = Year, y =Annual_Consumption)) +
  labs(x='Year',y='Electricity Consumption')+
  geom_smooth(method=lm, se=F)+
  geom_point()+geom_line()+scale_x_continuous(breaks = seq(2005, 2022, 1))
```

## Average Monthly Household Electricity Consumption (2005-2022)

```{r,warning=FALSE,message=FALSE}
Monthly <- read_excel("damand data/Each month temperature, average consumption.xlsx")
Monthly$Month <- factor(Monthly$Month, levels = 
                          c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))
ggplot(Monthly, aes(x = Month, y = `Average Monthly Household Electricity Consumption (kWh)`, fill = Month)) + geom_boxplot() +
  scale_fill_discrete(name = "Month") +
  labs(x = "Month", y = "Average Monthly Household Electricity Consumption (kWh)")
```

## Average Monthly Temperature (2005-2022)

```{r,warning=FALSE,message=FALSE}
Monthly <- read_excel("damand data/Each month temperature, average consumption.xlsx")
Monthly$Month <- factor(Monthly$Month, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))
ggplot(Monthly, aes(x = Month)) +
  geom_boxplot(aes(y = `Mean temperature`, fill = Month), alpha = 0.5) +
  labs(x = "Month", y = "Temperature", fill = "Month") +
  scale_fill_manual(values = 
                      c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#999999", "#000000", "#FFC0CB", "#8A2BE2", "#A52A2A"))
```

```{r,warning=FALSE,message=FALSE,include=FALSE}
library(readxl)
Monthly <- read_excel("damand data/Each month temperature, average consumption.xlsx")
cor(Monthly$`Mean temperature`, 
    Monthly$`Average Monthly Household Electricity Consumption (kWh)`)

test <- cor.test(Monthly$`Mean temperature`, 
Monthly$`Average Monthly Household Electricity Consumption (kWh)`)
test


library(ggplot2)
ggplot(Monthly) +
  aes(x = `Mean temperature`, y = `Average Monthly Household Electricity Consumption (kWh)`) +
  geom_point(colour = "#0c4c8a")+
  xlab("Average Monthly Temperature")
  theme_minimal()
```

## Correlation between Temperature and Consumption

```{r,warning=FALSE,message=FALSE}
library('ggside')
library(ggstatsplot)
ggscatterstats(
  data = Monthly,
  x = `Mean temperature`,
  y = `Average Monthly Household Electricity Consumption (kWh)`,
  xlab = 'Monthly Temperature',
  bf.message = FALSE
)
```

## Monthly Electricity Consumption by House Type

```{r,warning=FALSE,message=FALSE}
library(readxl)
HousingType <- read_excel("damand data/MonthlyConsumptionByHousingType.xlsx")
ggplot(HousingType, aes(x = factor(Month, levels = 1:12), y = AverageMonthlyHouseholdElectricityConsumption, fill = factor(Room_type))) +
  geom_boxplot() +
  scale_fill_manual(values = c("#FFC0CB", "#00BFFF", "#7FFF00", "#FF8C00", "#FFD700", "#BA55D3")) +
  facet_wrap(~ Housing_Type, scales = "free_y") +
  labs(x = "Month", y = "Average Monthly Household Electricity Consumption") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r,warning=FALSE,message=FALSE,include=FALSE}
library(dplyr)
library(readxl)
library(lubridate)
library(ggplot2)
mydata <- read_excel("damand data/Demand_Data_Monthly_compiled.xlsx", sheet = "Demand_Data_Monthly_compiled")
mydata_filtered <- mydata %>%
  filter(Area == "Whole Country") %>%
  mutate(Year_Month = ymd(paste0(Year, "-", Month, "-01"))) %>%
  filter(Year_Month >= ymd("2019-08-01") & Year_Month <= ymd("2022-06-01"))
```

## Pre, During, After Covid Household Electricity Consumption (2019/8-2022/7)

```{r,warning=FALSE,message=FALSE}
ggplot(data = mydata_filtered, aes(x = Year_Month, y = Monthly_Consumption)) +
  geom_area(fill = "blue") +
  xlab("Time") +
  ylab("Monthly Consumption") +
  scale_x_date(date_breaks = "1 month", date_labels = "%Y/%m",
               limits = c(ymd("2019-08-01"), ymd("2022-06-01")),
               expand = c(0, 0)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        plot.margin = unit(c(2,1,2,1), "cm"))

```
